---
title: "HW1"
author: "Jered Willoughby"
date: "3/22/2019"
output: word_document
---

#1 How many columns are in a 2×n matrix? How many rows? Give an example in R.
The answer to question 1 is the matrix has 2 rows and n number of columns. In order to display this in R, we will have to find a value for the n/column designator. I will choose n=3.

```{r}
A = matrix(c(3,2,1,1,2,3), ncol=3, byrow=T)
A
```

#2 Matrix Product
The answer is displayed by the R chunk below, please see. I went ahead and included dimensions before performing matrix multiplication.
```{r}
S = matrix(c(2,-1), ncol=2, byrow=T)
S
D = matrix(c(1,1,2,0), ncol=2, byrow=T)
D
dim(S)
dim(D)
S%*%D
```

#3 Matrix Product
The question’s function is included in the chunk below, please see. I went ahead and included dimensions before performing matrix multiplication. This matrix multiplication problem is a non comformable system which will not compute properly. Therefore, I removed the function and replaced it with an explanation passed to the variable Y.
```{r}
Q = matrix(c(1,0,2,0), ncol=2, byrow=T)
Q
W = matrix(c(2,-1), ncol=2, byrow=T)
W
dim(Q)
dim(W)
Y = 'Q%*%W is non-conformable'
Y
```

#4 Matrix Inverse
The inverse is not defined if the determinant of matrix is equal to zero. I showed this in the following chunk and passed the explanation to the variable Y.
```{r}
Z = matrix(c(1,0,2,0), ncol=2, byrow=T)
Z
detZ = det(Z)
detZ
Y = 'Zinv = solve(Z) - system is exactly singular'
Y
```

#5 Convert this covariance matrix into the corresponding correlation matrix (using R).
First, I created the matrix based on the original. Then I used the R function that corresponds the the equation provided from the lecure. Please see the following chunk. There was no specification on rounding which I tried but didn’t have success.
```{r}
cov = matrix(c(3.87, 2.81, 3.14, 3.50, 2.81, 2.12, 2.26, 2.56, 3.14, 2.26, 2.65, 2.83, 3.50, 2.56, 2.83, 3.23), ncol=4, byrow=T)
cov
cov2cor(cov)
```

#6 Find the euclidean distance matrix for the rows of the data in R.
To determine the distance in this problem, I had to determine the equation and plug in the proper R functions. The following chunk of code is what I came up with.
```{r}
love <- read.csv("http://tiny.cc/isqs6350_hus_wife")
love
m <- as.matrix(dist(love, upper=T))
D <- apply(m, 2, mean)
n <- length(D)
D <- n/(n-1)*D
D
```

