---
title: "HW2"
author: "Jered Willoughby"
date: "3/28/2019"
output: word_document
---
#1 Chi Squared - Examination of the multivariate normality of pottery data.
```{r}
#Load library and set the data frame
data(pottery, package ="HSAUR2")
x = pottery[,-10] # excluding "kiln"
# Following the example of Mahalanobis Distance - plot chi sq. 
xbar = colMeans(x)
S = cov(x)
d2 = mahalanobis(x,xbar,S)
quantiles = qchisq((1:nrow(x)-1/2)/nrow(x), df = ncol(x))
sd2 = sort(d2)
plot(quantiles, sd2, xlab=expression(paste(chi[3]^2,"Quantile")), ylab="Ordered Square distances")
abline(a = 0, b = 1)

```

After performing a multivariate analysis on the pottery dataset, we see that there are outliers past 20 with increasing mahalonobis distance.

#2 Bivariate boxplot and correlation before and after outlier removal.

```{r}
library(MVA)
data("USairpollution",package="HSAUR2")
df=USairpollution
# examine the scatterplots with labels
plot(USairpollution$temp, USairpollution$wind,
     xlab="Average annual temperature F",
     ylab="Average annual wind speed (mph)",
     pch = 20)
text(USairpollution$temp, USairpollution$wind, cex=0.8,
     labels=abbreviate(row.names(USairpollution)))

plot(USairpollution$temp, USairpollution$precip,
     xlab="Average annual temperature F",
     ylab="Average annual Precipitation",
     pch = 20)
text(USairpollution$temp, USairpollution$precip, cex=0.8,
     labels=abbreviate(row.names(USairpollution)))

# set dataframes and create bivariate boxplots
df1 = USairpollution[, c("temp","wind")]
df2 = USairpollution[, c("temp","precip")]

bvbox(df1, xlab="Average Annual Temperature F", ylab="Average Annual Wind Speed (mph)")
text(USairpollution$temp, USairpollution$wind, cex=0.8,
     labels=abbreviate(row.names(USairpollution)))

bvbox(df2, xlab="Average Annual Temperature F", ylab="Average Annual Precipitation")
text(USairpollution$temp, USairpollution$precip, cex=0.8,
     labels=abbreviate(row.names(USairpollution)))

#Set outlier data/labels
lab1 = c("Miami","Phoenix")
lab2 = c("Miami","Phoenix","Albuquerque","Denver")
outcity1 = match(lab1, rownames(USairpollution))
outcity2 = match(lab2, rownames(USairpollution))

#Run correlation before removal of outliers.
cor(df$temp, df$wind)
cor(df$temp, df$precip)

#Run correlation after removal of outliers.
cor(df$temp[-outcity1], df$wind[-outcity1])
cor(df$temp[-outcity2], df$precip[-outcity2])
```
We can see from the correlation of temp and wind that they have a weak, negative causal relationship. Temp and precip have a weak, possitive causal relationship. After the outlier were identified and removed, correlation between temp and wind become less while temp and precip increased to a stronger causal relationship.
#3a Banknote dataset - Construct univariate kernel estimates (Gaussian kernel) of the distributions of these two variables (two graphs).
```{r}
#Examine banknote dataset by reading the url.csv file
banknote = read.csv("http://westfall.ba.ttu.edu/isqs6348/Rdata/swiss.csv")

mydata1 = banknote[,c(1,5,7)]

#plot density using gaussian kernel
plot(density(mydata1$bottom_margin, bw = 0.3, kernel = "gaussian"))
plot(density(mydata1$diag_length, bw = 0.35, kernel = "gaussian"))
```
#3b Banknote dataset - Using the bivariate Gaussian kernel, estimate the bivariate density of the two variables
```{r}
#Using the KernSmooth library, make a contour and 3D plot
library("KernSmooth")
mydata2 = banknote[,c(2,4)]

density = bkde2D(mydata2, bandwidth = 0.1)
plot(mydata2, xlab = "Banknote Length", ylab = "Banknote Right Width", main = "Contour of Banknote Variables")
contour(x=density$x1, y=density$x2, z=density$fhat, add=TRUE)
persp(x=density$x1, y=density$x2, z=density$fhat,
      xlab = "Banknote Length", ylab = "Banknote Right Width", zlab= "density", main = "3D density", phi=30)
```
#3c Banknote dataset - Plot the scatterplot, highlighting points with different colors according to whether the bills are genuine or counterfeit
```{r}
#Using the same banknote dataset, use a color indicator to differentiate between counterfit bills.
mydata2 = banknote

plot(mydata2[,c(2,4)], col = mydata2[,1])
label = levels(mydata2[,1])
legend("topright", label, pch=1, col = 1:2, cex=0.8)

library(ResourceSelection)
kdepairs(mydata2[,c(2,4)])
```

