---
title: "R Assignment 7"
author: "Jered Willoughby"
output: html_document
word_document: default
---

A quality characteristic of interest for a tea-bag-filling process is the weight of the tea in the individual bags. The label weight on the package indicates that the mean amount is 5.37 grams of tea in a bag. Problems arise if the bags are under-filled or if the mean amount of tea in a bag exceeds the label weight. The accompanying data are the weights, in grams, of a sample of 50 tea bags produced in one hour by a single machine (data file Teabags.csv).

```{r}
data <- read.csv("https://goo.gl/ZCVUpc")
mean = mean(data$Teabags)
mean
sd = sd(data$Teabags)
sd
```

1) Construct a 95\% confidence interval estimate for the population mean weight of the tea bags. Interpret the interval. 

```{r}
n = 50
df= n-1
alpha = 0.05
error = qt(0.975, df)*sd/sqrt(n)
mean - error
mean + error
```

We're 95% confident that the mean of the individual tea bags will fall between 5.47 and 5.53.

2) Is the company meeting the requirement set forth on the label that the mean amount of tea in a bag is 5.37 grams?

No, it is evident from the initial average calculation (5.5014) and the confidence interval [5.471323 - 5.531477] that the labeled mean amount is under the actual weight of the tea bag.

3) Explain how to understand the “95%” of the interval via simulation. Use simulation in your answer. 
```{r}
set.seed(123)
n = 10
NSIM=10000
rv=rnorm(n*NSIM,5.5014,1)
mu = 5.5014
sd = 0.1058
alpha = 0.05
rvm=matrix(rv,ncol=n, byrow=TRUE)
ybars = rowMeans(rvm)
sdevs=apply(rvm,1,sd)
lower=ybars - qt(1-alpha/2,n-1)*sdevs/sqrt(n)
upper=ybars + qt(1-alpha/2,n-1)*sdevs/sqrt(n)

head(cbind(ybars,sdevs,n,lower,upper,mu), 30)
mean((lower<mu) & (mu<upper))
```
From the simulation we can see that proportions are in the range (0.9515), which is the 95% confidence interval. The majority of the upper and lower bound (95%) will fall in the range.

Note: Realize, of course, that the distributions that produce the data cannot possibly be normal, but do the simulation using normal distribution anyway.
