---
title: "RAssignment2"
author: "Jered Willoughby"
date: "9/6/2018"
output: html_document
---

Use the TTU graduate student exit survey data. 

```{r}
grad <- read.csv("http://tiny.cc/isqs6350_grad", header = T)
attach(grad)

head(COL)
```

Two variables of interest are FacTeaching, a 1,2,3,4,5 rating of teaching at TTU by the student, and COL, the college from which the student graduated. Perform a correspondence analysis of these two variables as follows. 

1. Construct the contingency table showing counts of students in all combinations of these two variables.

```{r}
table(COL, FacTeaching)
```
2. Construct a contingency table showing the proportion of students in all combinations of these two variables (we call this marginal ).

```{r}
t = table(COL, FacTeaching)/length(COL)

round(t,3)
```

3. What is the probability that a randomly selected student is from college of business administration (BA)?

```{r}
rowSums(t)
```

The probability that a randomly selected student is from college of business administration (BA) is 0.131368631.

4. What is the probability that a randomly selected student is from BA and rates the teaching quality by 5?

The probability that a randomly selected student is from BA and rates the teaching quality by 5 is 0.004.

5. Given that a randomly selected student is from BA, what is the probability that he/she rates the teaching quality by 5?

The that a randomly selected student is from BA and rates the teaching quality by 5 is 0.2519.

6. Given that a randomly selected student is from college of education (ED), what is the probability that he/she rates the teaching quality by 5? What is your conclusion about the difference between the quality of teaching in BA and ED.

Given that a randomly selected student is from college of education (ED), the probability that he/she rates the teaching quality by 5 is 0.3865. It's evident that the student rated quality of teaching in the education department far exceeds that of the business department.

7. Given that a randomly selected student rates the teaching quality by 5, what is the probability that he/she is graduated from BA?

Given that a randomly selected student rates the teaching quality by 5, the probability that he/she graduated from BA is 0.1157.

